Carbonate chemistry at Ny-Ålesund

### 2023-03-13 awipev-CO2.Rmd
more fine-tuning of figs

# pCO2 deltas
g <-  pco2_delta_plt / pco2_4_delta_plt
g <- g + plot_annotation(tag_levels = 'A') & 
                             theme(plot.tag = element_text(face = "bold"))
g
ggsave(filename = "figures/deltas_pco2.png", plot = g, width = 15, height = 20, units = "cm")
ggsave(filename = "figures/essd/deltas_pco2.pdf", plot = g, width = 20, height = 20, units = "cm")
```

@@

# For paper
size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
# temp_insitu_11m
ts_air_sea <- air_sea_month %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000), na.rm = TRUE) +
  geom_col(colour="blue", fill = "blue",  alpha = alpha) +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  Mytheme(size_labs = size_labs) +
  theme(plot.margin = margin(t = 0.2, r = 0.2, b = 0.2, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea
ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 20, units = "cm")
#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
```

@@

ts_oa <- tmp %>%
  ggplot(aes(x = datetime, y = OmegaAragonite), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  ylim(0, 3) +
  labs(title="",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
  Mytheme(size_labs = size_labs)
ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
ggsave(filename = "figures/essd/OmegaAragonite.pdf", plot = ts_oa, width = 15, height = 10, units = "cm")

```
### Whole time series plot

>>>>

# pCO2 deltas
g <-  pco2_delta_plt / pco2_4_delta_plt
g <- g + plot_annotation(tag_levels = 'A') & 
                             theme(plot.tag = element_text(face = "bold"))
g
ggsave(filename = "figures/deltas_pco2.png", plot = g, width = 15, height = 20, units = "cm")
ggsave(filename = "figures/essd/deltas_pco2.pdf", plot = g, width = 15, height = 20, units = "cm")
```

@@

# For paper
size_point <- 1.5 # size of data points
alpha <- 1 #transparency
size_labs <- 14 # font size labels
# temp_insitu_11m
ts_air_sea <- air_sea_month %>%
  ggplot(aes(x = montht, y = f_air_sea / 1000), na.rm = TRUE) +
  geom_col(colour="blue", fill = "blue",  alpha = alpha) +
  lims(y = c(-3, 0)) +
  geom_hline(yintercept = 0) +
  labs(title=NULL, 
       x="Month", 
       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
  Mytheme(size_labs = size_labs) +
  theme(aspect.ratio=0.5,
        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_air_sea
ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 15, height = 10, units = "cm")
#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
```

@@

ts_oa <- tmp %>%
  ggplot(aes(x = datetime, y = OmegaAragonite), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  ylim(0, 3) +
  labs(title=NULL,x="Time", y=latex2exp::TeX("\\textbf{$\\Omega_{aragonite}$}")) +
  Mytheme(size_labs = size_labs) +
    theme(aspect.ratio=0.5,
        plot.margin = margin(t = 0, r = 0.2, b = 0, l = 0.2, unit = "cm"),
        axis.title.x = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14),
        axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14)
        )
ts_oa
ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
ggsave(filename = "figures/essd/OmegaAragonite.pdf", plot = ts_oa, width = 15, height = 10, units = "cm")
```
### Whole time series plot
